\section*{Instructions for Writing a Midterm Report}

\marginnote{\newthought{These submissions are not an end in themselves}, but rather a means to an end. They serve as a scaffold for your thesis work, giving you a helpful yet decisive nudge to structure.}

\newthought{Begin with a concise overview of your project’s current status} compared to the plan you outlined earlier. 
Take this opportunity to reflect on your objectives and timeline, and discuss adjustments.

\newthought{Include an overview figure of your system, methods, or architecture.} This schematic should clearly illustrate the major components
 of your approach and how they interact. Think of it as the “big picture” figure that will 
 later appear in the introductory part of the Methods chapter of your thesis.


\newthought{Introduce the prototype, proof of concept or initial implementation work} you have completed. 
This may include pseudo code, initial experiments, dataset preprocessing, or system components. 
Demonastrate development activity by providing a deployment or a means to deploy and reproduce your work.


\newthought{Discuss any problems or challenges} you have encountered so far and explain how you have addressed them or plan to address them. 
This may include technical obstacles, methodological uncertainty, unexpected data issues, or changes in scope. You will not find a dedicated section for this in the template,
make sure to use marginnotes and introduce them as you go.


\newthought{Follow this template and maintain a clear, structured format.} Limit yourself to 4 pages, not counting figures or tables.
Proofread your work before submission.

