%% meta.tex -- Shared metadata and templates 
%% Author: Dr.-Ing. Mark Schutera

%%
% Default author information
%%
\newcommand{\defaultauthor}{Dr.-Ing. Mark Schutera}
\newcommand{\defaultpublisher}{Unfinished Lecture Notes}
\newcommand{\defaultlocation}{Germany, Planet Earth}


%%
% Copyright page template
%%
\newcommand{\makecopyright}[1][]{%
  \newpage
  \begin{fullwidth}
  ~\vfill
  \thispagestyle{empty}
  \setlength{\parindent}{0pt}
  \setlength{\parskip}{\baselineskip}
  
  Copyright \copyright\ \the\year\ \thanklessauthor
  
  \par\smallcaps{Published by \thanklesspublisher}
    
\par Licensed under the Creative Commons Attribution-NonCommercial 4.0 International License (``CC BY-NC 4.0''). 
You may not use this file for commercial purposes. 
You must obtain explicit permission from the author for uses beyond those permitted by this license. 
To view a copy of this license, visit \url{https://creativecommons.org/licenses/by-nc/4.0/}. 
Unless required by applicable law or agreed to in writing, distributed material is provided on an 
\smallcaps{``AS IS'' BASIS, WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND}, either express or implied. 
See the license for details.\index{License}
  
  \par\textit{First printing, \monthyear}
  \end{fullwidth}
}

%%
% Standard front matter structure
%%
\newcommand{\makestandardfrontmatter}{%
  \frontmatter
  \maketitle
  \makecopyright
}

%%
% Standard acknowledgment template
%%
\newcommand{\makeacknowledgment}[1]{%
  \cleardoublepage
  \chapter*{Acknowledgements}
  #1
}

%%
% Standard affirmation page template
%%
\newcommand{\makeaffirmation}[1][]{%
  \newpage
  ~\vfill
  \thispagestyle{empty}
  \setlength{\parindent}{0pt}
  \setlength{\parskip}{\baselineskip}

  \chapter*{Affirmation}

  Chances are high, that your institution or industrial partner requires a specific 
  affirmation statement to be included in your thesis. Please make sure to adapt the text below
  to your specific needs and requirements. This is just a general template.
  I hereby affirm that this thesis is my own work and that I have not used any sources or aids other than those indicated. 
  All passages taken from other works are clearly marked as such. I am aware that any false declaration may lead to legal consequences.

  \vspace{2em}
  \begin{flushright}
    \rule{0.66\linewidth}{0.5pt}

      \textit{\thanklessauthor}\\
      \textit{\defaultlocation, \monthyear}
  \end{flushright}
}

%%
% Standard introduction template
%%
\newcommand{\makeintroduction}[1]{%
  \cleardoublepage
  \chapter*{Abstract}
  #1
}

%%
% Standard dedication page template
%%
\newcommand{\makededication}[1]{%
  \cleardoublepage
  \thispagestyle{empty}
  ~\vfill
  \begin{doublespace}
  \noindent\fontsize{18}{22}\selectfont\itshape
  \nohyphenation
  #1
  \end{doublespace}
  \vfill
  \vfill
}


%%
% Standard tables command: Table of Contents, Figures, Tables, Equations, Abbreviations, Symbols. Yes, some of these are still missing in this template.
% Looking for a place to contribute - you found it!
%%
\newcommand{\makestandardtables}{%
  \cleardoublepage
  \listoffigures
  \cleardoublepage
  \listoftables
  }

%%
% Font options template
%%
\newcommand{\loadoptionalfonts}{%
  % Font options (uncomment if available)
  %\IfFileExists{bergamo.sty}{\usepackage[osf]{bergamo}}{}% Bembo
  %\IfFileExists{chantill.sty}{\usepackage{chantill}}{}% Gill Sans
  %\usepackage{microtype}
}